A non-contextual hidden variable model for quantum mechanics

### 2017-02-09 finalPaper.tex
/ ‘finalPaper.tex’
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’

contextuality is not a necessary feature of quantum statics (QS).

@@

consistent with QS  while remaining

@@

with QS} \label{fig:block}\end{figure}

@@

In this letter we have presented
non-multiplicativity as an alternative to
contextuality and as an essential signature of
quantumness at the kinematic level. {\color{red} Our result
points to a (quantum) dynamical study of contextuality which 
so far has effectively been analysed kinematically only.}
%Implications of quantum dynamics for
%our model and in general for the notion of
%non-multiplicativity need to be explored
%further.
%We expect this to provide new insights that will be useful
We expect {\color{red}our result} to provide new insights that will be useful
in the areas of foundations of QM and QIP.

>>>>

contextuality is not a necessary feature of quantum kinematics (QK).

@@

consistent with QK while remaining

@@

with kinematics of QM} \label{fig:block}\end{figure}

@@

In this letter we have presented
non-multiplicativity as an alternative to
contextuality and as an essential signature of
quantumness at the kinematic level. Our result
points to a (quantum) dynamical exploration of contextuality which 
so far has effectively been studied kinematically only.
%Implications of quantum dynamics for
%our model and in general for the notion of
%non-multiplicativity need to be explored
%further.
%We expect this to provide new insights that will be useful
We expect {\color{red}our result} to provide new insights that will be useful
in the areas of foundations of QM and QIP.
